Algorithmic and Economic Aspects of the Internet

### 2012-12-04 report/paper.tex
Fix the paper
Signed-off-by: Sam Phippen <samphippen@googlemail.com>
Paper update.
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

@@

Our implementation also seems to issue significantly fewer trades than would be
expected. Looking at the implemeentations of the other bots provided by D.
Cliff, it is not hard to see why. The implementations provided will always
return a trade when the bot has an order to fulfil (with the exception of the
Sniper bot which will make a shout on every round after a give threshold)
meaning these implementations have many more shouts on which to make profit.

@@

\begin{enumerate}
\item

\section{Analysing the other traders}

In this section we wanted to analyse the ZIP agent against all the others.
Based on the COMSM2006\cite{cliff:lecture} lecture about trading agents.
Specifically the lecture references an article written by D. Cliff which is
meant to show a case where ZIC traders will not converge to the equilibrium
price of the market\cite{cliff:minimalint}.

>>>>

Luke can you make this connect better

@@

Our implementation also seems to issue significantly fewer trades than would be
expected. Looking at the implementations of the other bots provided by D.
Cliff, it is not hard to see why. The implementations provided will always
return a trade when the bot has an order to fulfil (with the exception of the
Sniper bot which will make a shout on every round after a give threshold)
meaning these implementations have many more shouts on which to make profit.

@@

\section{ZIC versus ZIP in the square wave market}

Contrary to our initial intuitions, the previously described square wave market
conditions caused an interesting behaviour when comparing ZIP and ZIC in a one
versus one fashion. ZIC actually beat ZIP 65 out of 100 times when running this
test. The median profit for ZIC agents was 1793.5, beating ZIP's median profit
of 1487.25. Using the Wilcoxon test showed that this difference of medians was
statistically significant (p < 0.01).

In figure n we show the trades issued by each agent in one of our sample runs
with time within the trading session, along with the agent's limit price when
the trade was created.

--luke can you fill this out explaining why this happened

Even in this admittedly artificial environment it is interesting to note that
whilst in realistic environments the more advanced traders may dominate, in
obscenely volatile markets, this result may indicate that less intelligent
traders that do not introspect the market may be better at generating profit.

\section{Conclusions}

Whilst we attempted to implement the adaptive aggressive algorithm, it is
pretty clear based on the analysis presented in this paper that our
implementation falls short. Whilst it is able to trade more efficiently than
the Giveaway trader in one versus one cases, with a simple supply and demand
schedule, the results from the rest of the analysis presented indicate that our
agent would not be the one to use if one were desperately motivated to make
incredible profits.

We also analysed the case that produces worst case behaviour in our agent,
which is when it is placed against a shaver trading agent in a many versus many
fashion. In this case our agent is found to generate a small loss. This occurs
because of shaver's rapid descent to the mean (luke can you check this).

Finally we produced an analysis showing that in a very volatile market, the
less "intelligent" ZIP agent is able to generate more profit than the ZIC
agent. We posit this is because the trend analysis that ZIP attempts to make
cannot be accurate, due to the rapidly oscillating nature of the market.
